Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-15 ms.tex
IRIS reference, testing bare repository

With the advent of the Planck mission, we have an important opportunity to
revisit foreground predictions in light of their superb data. Brief Planck
background. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
doing so, we obtain $6.1'$ maps of dust temperature and optical depth. Because
we are using a model that has been validated using FIRAS data down to sub-mm
wavelengths, this model should be useful in constructing predictions of dust
emission over a very broad range of wavelengths. This includes low frequencies,
which \cite{planckdust} admit their model does not adequately fit, and also
data near the peak of the dust SED, for example Akari. We also anticipate 
the optical depth map we derive will be useful as a comparison for extinction
estimates based directly upon optical/NIR observations of stars.

@@

\subsection{Comparison to Planck Collaboration Dust Map}
%striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping

>>>>

With the advent of the Planck mission, we have an important opportunity to
revisit foreground predictions in light of their superb data. Brief Planck
background. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
doing so, we obtain $6.1'$ maps of dust temperature and optical depth. Because
we are using a model that has been validated using FIRAS data down to sub-mm
wavelengths, this model should be useful in constructing predictions of dust
emission over a very broad range of wavelengths. This includes low frequencies,
which \cite{planckdust} admit their model does not adequately fit, and also
data near the peak of the dust SED, for example \AKARI. We also anticipate 
the optical depth map we derive will be useful as a comparison for extinction
estimates based directly upon optical/NIR observations of stars.

@@

\subsection{Comparison to Planck Collaboration Dust Map}
%striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
An important difference between our maps and those of \cite{planckdust} is our 
use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}.
